---
title: "Time series clustring and classification"
output: html_notebook
---

data discription
https://kdd.ics.uci.edu/databases/synthetic_control/synthetic_control.data.html

measuring somthing(metric) in different times (60) 


task and problem is to recognize sort of series 
https://kdd.ics.uci.edu/databases/synthetic_control/synthetic_control.clustering.html
how many trend can be identified in our observations 


data
https://kdd.ics.uci.edu/databases/synthetic_control/synthetic_control.data

data read
```{r}
data <- read.table(file.choose(), header=F, sep = "")
str(data)
```

plot
```{r}
plot(data[,60], type = 'l')

```

for plotting a sample of each pattern with systematic sampling 
```{r}
j <- c(5,105, 205, 305,405, 505)
sample <- t(data[j,])
plot.ts(sample,
        main="Time -series Plot",
        col='blue',
        type= 'b')

```

data prepration 
systematic random sample of 10 which means 60 bservation out of 600 observation has been choosed for 60 varible(times)

```{r}
n <- 10 
s <- sample(1:100, n)
i <- c(s, 100+s, 200+s, 300+s, 400+s, 500+s)
d <- data[i, ]
str(d)
```

pattern or nameing trends 
```{r}
pattern <- c(rep('Normal',n),
             rep('Cyclic',n),
             rep('Increasing',n),
             rep('Decreasing',n),
             rep('Upward',n),
             rep('downward',n))
```

calculation of distances by Derivative Dynamic Time Warping
```{r}
library(dtw)
distance <- dist(d, method = "DTW")
```

Hierarchical clustring 
```{r}
hc <- hclust(distance, method='average')
plot(hc, 
     labels = pattern,
     cex=0.7,
     hang=-1,
     col='blue')
rect.hclust(hc, k=4)

```

for identematictifiying number of clusters 


Classification 
Data preparation 
instead of systematic random sampling all data has been considered 

```{r}
pattern100 <- c(rep('Normal',100),
             rep('Cyclic',100),
             rep('Increasing',100),
             rep('Decreasing',100),
             rep('Upward',100),
             rep('downward',100))
newdata <- data.frame (data, pattern100)
str(newdata)
```

classfication with decision tree
```{r}
library(party)
tree <- ctree(pattern100~.,newdata)
tree
```
as it is shown there is 25 terminal nodes

classification performance 
```{r}
tab <- table(predicted = predict(tree,newdata), actual=newdata$pattern100)
tab
sum(diag(tab))/sum(tab)
```
it is shown that this classification is above 95% accurate 




